---
title: "Vignette for Stats"
author: "Ivan Ma"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ma0029Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```

# Purpose

The purpose of "FALL224753ma0029" is to store functions used throughout the course into one package. These functions provide statistical value in some way. Creating plots, estimating values, solving specific problems, etc. In this vignette, some of the functions contain within the package will be used and describe in brief.


# Functions

```{r setup}
library(FALL224753ma0029)
```

## ntickets

Ntickets() attempts to simulate the problem that airlines have of overbooking more tickets then they have seats to compensate for people not showing up. 

N = number of seats on the plane

p = probability of someone showing up

gamma = probability of overbooking

nc = number of tickets that should be sold using the normal approximation

nd = number of tickets that should be sold using the binomial distribution 

```{r}
par(mar=c(1,1,1,1))
FALL224753ma0029::ntickets()
```

## scatterhist

Scatterhist() creates histograms for the x and y values as well as plots y ~ x.

```{r}
with(fire, scatterhist(DISTANCE,DAMAGE, xlab="DISTANCE"))
```

## myncurve

myncurve() creates a visual of the normal distribution and the corresponding lower-tail probability given a value.

```{r}
myncurve()
```

## myboot2

myboot2() creates a bootstrap sample statistic given some function and data set. The example below uses the `DAMAGE` variable from the `fire` data set, the `mean` function, and `alpha = 0.05`

```{r}
myboot2(x=fire$DAMAGE)
```
